\clearpage
\renewcommand{\bibname}{Referencias Bibliográficas}
\begin{singlespacing}
\begin{sloppypar}
\raggedright
\setlength{\emergencystretch}{3em}

ADEX. (2023). \textit{Evolución del mercado mundial y nacional de palta}.
\url{https://cien.adexperu.org.pe/wp-content/uploads/2024/11/CIEN_NSIM1_Julio_2023_Palta.pdf}

\bigskip\noindent
Capuñay, M., Rivas, I., \& Díaz, E. (2025). Hass avocado and profitability in
the crisis: A critical look at Peruvian exports (2018--2022). \textit{Proceedings
of the LACCEI International Multi-Conference for Engineering, Education, and
Technology}. \url{https://dx.doi.org/10.18687/LEIRD2025.1.1.616}

\bigskip\noindent
Chen, J., Li, X., \& Wang, Y. (2023). A genetic algorithm optimized hybrid model
for agricultural price forecasting based on VMD and LSTM network.
\textit{Scientific Reports, 13}(1), Article 9932.
\url{https://doi.org/10.1038/s41598-025-94173-0}

\bigskip\noindent
Xia, C. (2024). Comparative analysis of ARIMA and LSTM models for
agricultural product price forecasting. \textit{Highlights in Science,
Engineering and Technology, 85}, 123--130.
\url{https://doi.org/10.54097/8q6nx369}

\bigskip\noindent
Kaggle. (s.f.). \textit{Avocado prices}.
\url{https://www.kaggle.com/datasets/neuromusic/avocado-prices}

\bigskip\noindent
Pantaleón, L., Montes, I., Azañero, R., Maco, B. H., Capristán, A.,
Del-Carpio, H., \& Rázuri Rubio, H. (2024). \textit{Sostenibilidad de las
empresas exportadoras de palta en el Perú a nivel internacional (2012--2023)}.
Repositorio Alicia CONCYTEC. \url{https://doi.org/10.18687/LACCEI2024.1.1.514}

\bigskip\noindent
Torres, A. (2022). \textit{Propuesta de mejora de la cadena de suministros de
la palta mediante el uso de herramientas de análisis de series de tiempo}
[Tesis, Pontificia Universidad Católica del Perú].
\url{https://tesis.pucp.edu.pe/items/01383649-c07a-4adc-b44f-acb6ca163488}

\bigskip\noindent
UNData. (s.f.). \textit{FAOSTAT agricultural data}.
\url{https://data.un.org/Data.aspx?d=FAO\&f=itemCode\%3A572}

\bigskip\noindent
Velásquez, F., Cardona, R., Sierra, S., \& Jiménez, E. (2025). Methodological
proposal for market risk quantification: A case study of the Hass avocado.
\textit{Revista de Economia e Sociologia Rural, 63}(2), e234567.
\url{https://doi.org/10.1590/1806-9479.2025.291499}

\bigskip\noindent
Zhang, L., Feng, L., \& Li, R. (2025). \textit{Avocado price prediction using a
hybrid deep learning model}. arXiv preprint arXiv:2505.09907.
\url{https://doi.org/10.48550/arXiv.2505.09907}

\bigskip\noindent
ComexPer\'u. (2025). \textit{Paltas y diversificaci\'on de mercados}.
\url{https://www.comexperu.org.pe/articulo/paltas-y-diversificacion-de-mercados}

\bigskip\noindent
MIDAGRI. (2024). \textit{Exportaci\'on de palta super\'o las 36 mil toneladas
en primer bimestre de 2024}.
\url{https://www.gob.pe/institucion/sse/noticias/930071-midagri-exportacion-de-palta-supero-las-36-mil-toneladas-en-primer-bimestre-de-2024}

\bigskip\noindent
Murugesan, R., Mishra, E., \& Krishnan, A. H. (2022). Forecasting agricultural
commodities prices using deep learning-based models: Basic LSTM, Bi-LSTM,
stacked LSTM, CNN LSTM, and convolutional LSTM. \textit{International Journal
of Sustainable Agricultural Management and Informatics, 8}(3), 242--277.
\url{https://doi.org/10.1504/IJSAMI.2022.125757}

\bigskip\noindent
PromPer\'u Exportemos. (2026). \textit{Aguacates (paltas), frescas o secas:
subpartida 0804400000}.
\url{https://exportemos.pe/descubre-oportunidades-de-exportacion/producto/palta-0804400000}

\bigskip\noindent
Reis Filho, I. J., Marcacini, R. M., \& Rezende, S. O. (2022). On the
enrichment of time series with textual data for forecasting agricultural
commodity prices. \textit{MethodsX, 9}, 101758.
\url{https://doi.org/10.1016/j.mex.2022.101758}

\bigskip\noindent
Vittery-Flores, E. R., \& Colchao-Ccahuana, R. (2023). Situaci\'on actual y
perspectivas de la producci\'on de palta (\textit{Persea americana}) peruana en
el contexto del comercio internacional. \textit{Ingenier\'ia Industrial, 44},
157--178. \url{https://doi.org/10.26439/ing.ind2023.n44.6316}

\end{sloppypar}
\end{singlespacing}

\FloatBarrier
